Response to reviewers

### 2022-02-16 response/response1.Rmd
Add longitudinal version of .

\begin{description}
\item[Editor and Reviewer 1:] \textcolor{violet}{How is this manuscript relevant for teachers and/or students in statistics and data science?}

The introduction has been re-written with an emphasis on how this work should be interesting for teachers and students of data science and statistics.

\item[Reviewer 1:] \textcolor{violet}{I don't see the direct relevance of this manuscript with the readership of JSDSE. I think this could be a valuable paper to describe the author(s) R package and would have value for researchers using the NLSY79 dataset. I am not convinced that JSDSE is the appropriate venue for this. I do not see this manuscript being engaging enough to be used in the classroom as a case study in data cleaning.}

It is commonly said 80\% of a data analysts/scientist's work is on data cleaning/preperation so we believe that shedding more light in this aspect of work is an important for students to be aware of. We believe that there are often subjective decisions made in the process (as we have done) which can be used as a conversation for transparency and reproducibility in class based on a real case study.

\item[Reviewer 3:] \textcolor{violet}{The authors prominently cite (Chatfield 1985) for the definition of the term “IDA”. However, Chatfield fairly explicitly defines IDA to be a data summarizing and scrutinizing process; not a cleaning, scrubbing, or munging process. It seems curious to me that the whole paper is framed as being “IDA” based on the author’s unsupported statement that data cleaning should be considered party of IDA.}

Yes, there is grey area in these three activities. Thanks for pointing out Chatfield's original viewpoint, which differs from Huebner et al's. We have revised this paragraph to de-emphasize cleaning as being part of IDA. We have kept the explanation of the terminology of IDA and EDA because we think this is important to clarify for teaching purposes.

\item[Reviewer 3:] \textcolor{violet}{My suggestion is that the authors reconfigure this paper to be presented as a pure case study. I believe the work that has been done is valuable: the data cleaning process is often messy and unplanned, so a case study like this on a popular dataset would provide an excellent educational resource.}

We have kept the case study frame of mind but have re-cast the paper so that it focuses on the importance of this type of activity for teaching of statistics and data science. 
\end{description}

@@

XXX We need to review this literature. It's not true that we have ignored it, the main reference is Dasu! But we need to decide whether there is more that we shoudl cite.

Outlier detection ???

@@

We thank the reviewer for pointing out to us that the data contains information on the work experience -- this additional data is added in the extraction of the data in Figure 1. This information was compared with Singer & Willet's original data. Comparison shown in Figure X shows that the information does not match up, however, there is a high correlation between the variables.

\begin{description}
\item[Reviewer 1:] \textcolor{violet}{This sentence is unclear. What is dplyr used for? Are there tidyverse packages used but not mentioned? If not, splitting this sentence into two may make it clearer which package is used to what purpose. Also, I haven't tried it in code, but I imagine that the data could be tidied as described just using pivot\_longer, at least for the job number, year, and wage data. In other words, I don't see why dplyr or stringr would be needed for the data described on page 6.}

We did not go into great detail about the packages used as the whole code is available as a vignette within the package. We realise that this was not available to the reviewers due to the requirement of a blind review. To circumvent this, we have added the vignettes as supplementary materials. 
\end{description}

@@

* We have fixed the sentences and the reference. XXX Which one?

@@

* We have split the sentences and described the use of each package mentioned.

@@

@@

* There is no individuals up to 8th grade in the refreshed dataset as we only filtered the high school dropouts (started from 9th grade ,i.e., high school grade). The plausible reasons for the differences are we might have different definition of high school dropouts with the original data and the corresponding individual back to high school after they dropped out so that their highest grade completed is 12th grade.

@@

@@

\begin{description}
\item[Reviewer 2:]\textcolor{violet}{I think there is a narrative step missing here, which is that looking at those samples led you to look at plots that show values for the wage variable over all participants and all years. The phrase “the summary plots” was not enough description for me to know what to expect when I flipped to Figure 3. Please be explicit about what the three plots were, why they were made, and what you were looking for. I think there is another narrative step missing about Figure 3C, which is that after you saw there were outliers you tried to identify which respondents had the extreme values. Again, please spell this out in the text. When you return to the plots for the entire dataset in Figure 5, please make parallel comments.}
\end{description}

@@

* We removed this sentence as we already have the `yr_workforce` variable which is calculated from the year of the individual start working.

@@

@@

We agree that this level of precision was not necessary. We have modified Table 2 so percentages are to the nearest 1 percent and total percentage (=100%) is omitted.

@@

* These are two different variables. We have made this easier to follow in the manuscript as: [FILL]

@@

* Yes, the data is collected on a yearly basis. However, according to the database, the highest grade completed variable is revised as in May 1st of each survey year. Thus, we mentioned as the revised May data. In the revised version, we only mention it as revised data to avoid confusion.

>>>>

\begin{description}
\item[Editor and Reviewer 1:] \textcolor{violet}{How is this manuscript relevant for teachers and/or students in statistics and data science?}
\end{description}

* The introduction has been re-written with an emphasis on how this work should be interesting for teachers and students of data science and statistics.

\begin{description}
\item[Reviewer 1:] \textcolor{violet}{I don't see the direct relevance of this manuscript with the readership of JSDSE. I think this could be a valuable paper to describe the author(s) R package and would have value for researchers using the NLSY79 dataset. I am not convinced that JSDSE is the appropriate venue for this. I do not see this manuscript being engaging enough to be used in the classroom as a case study in data cleaning.}
\end{description}

* It is commonly said 80\% of a data analysts/scientist's work is on data cleaning/preperation so we believe that shedding more light in this aspect of work is an important for students to be aware of. We believe that there are often subjective decisions made in the process (as we have done) which can be used as a conversation for transparency and reproducibility in class based on a real case study.

\begin{description}
\item[Reviewer 3:] \textcolor{violet}{The authors prominently cite (Chatfield 1985) for the definition of the term “IDA”. However, Chatfield fairly explicitly defines IDA to be a data summarizing and scrutinizing process; not a cleaning, scrubbing, or munging process. It seems curious to me that the whole paper is framed as being “IDA” based on the author’s unsupported statement that data cleaning should be considered party of IDA.}
\end{description}

* Yes, there is grey area in these three activities. Thanks for pointing out Chatfield's original viewpoint, which differs from Huebner et al's. We have revised this paragraph to de-emphasize cleaning as being part of IDA. We have kept the explanation of the terminology of IDA and EDA because we think this is important to clarify for teaching purposes.

@@

* **Need help** XXX We need to review this literature. It's not true that we have ignored it, the main reference is Dasu! But we need to decide whether there is more that we should cite.

@@

* **NEED HELP**

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{The authors explain the complication of the “years of job experience” variable being unavailable in the raw data. This information is available in the NLSY79 data accessor; it seems to simply have been not selected in the initial data download by the authors.
Given that the stated goal is to recreate the textbook data, this seems like a glaring oversight.
It also leads to Fig 7 (Now Figure 8) being essentially meaningless: we are unsurprised that salaries are higher with more years of experience, and we are unsurprised that salaries go up over the years with both age of employee and inflation. The positive slope of these two different plots does not mean they are related to each other in any way.}
\end{description}

* We thank the reviewer for pointing out to us that the data contains information on the work experience -- this additional data is added in the extraction of the data in Figure 1. This information was compared with Singer & Willet's original data. Comparison shown in Figure 7 shows that the information does not match up, however, there is a high correlation between the variables.

* **NEED HELP in responding comments on Figure 8.**

\begin{description}
\item[Reviewer 3:] \textcolor{violet}{My suggestion is that the authors reconfigure this paper to be presented as a pure case study. I believe the work that has been done is valuable: the data cleaning process is often messy and unplanned, so a case study like this on a popular dataset would provide an excellent educational resource.}
\end{description}

* We have kept the case study frame of mind but have re-cast the paper so that it focuses on the importance of this type of activity for teaching of statistics and data science.

@@

* We have fixed the sentences and the reference, it is reflected on the last paragraph in page 3.

@@

* We did not go into great detail about the packages used as the whole code is available as a vignette within the package. Also, for the blind review purpose, we have made all of the code and the raw dataset available to reviewers and it is not depend on the R package we created. The reviewers can see the data processing code and run it to also see the reproducibility of the code. Besides, in the paper, we have split the sentences and described the use of each package mentioned.

@@

* **NEED HELP**

@@

* There are 108 individuals up to 8th grade in the refreshed dataset, compared to 366 individuals in the original dataset. The plausible reason for this difference is that some people have had GED after the period covered in the original dataset.

@@

* We have it more explicit as per the reviewers' comments.

@@

* **NEED HELP**

\begin{description}
\item[Reviewer 2:]\textcolor{violet}{I think there is a narrative step missing here, which is that looking at those samples led you to look at plots that show values for the wage variable over all participants and all years. The phrase “the summary plots” was not enough description for me to know what to expect when I flipped to Figure 3. Please be explicit about what the three plots were, why they were made, and what you were looking for. I think there is another narrative step missing about Figure 3C, which is that after you saw there were outliers you tried to identify which respondents had the extreme values. Again, please spell this out in the text. When you return to the plots for the entire dataset in Figure 5, please make parallel comments.}
\end{description}
* **NEED HELP**

@@

* We removed this sentence as we already have the `yr_wforce` variable which is calculated from the year of the individual start working.

@@

* We have filter the x-axis of the refreshed data set until 1994, so they are comparable.

@@

* We agree that this level of precision was not necessary. We have modified Table 2 so percentages are to the nearest 1 percent and total percentage (=100%) is omitted.

@@

* These are two different variables. We have made this easier to follow in the manuscript as we add explanation on what the target data is (See Subsection 2.2: Target Data).

@@

<!--* Yes, the data is collected on a yearly basis. However, according to the database, the highest grade completed variable is revised as in May 1st of each survey year. Thus, we mentioned as the revised May data. In the revised version, we only mention it as revised data to avoid confusion.-->

*  The database has the variable of `the highest grade completed ever`. Thus, we use this variable for `hgc` instead of calculating it from the`hgc` the respondents answer for each round of the survey. Besides, we also add new variable `grade`, which is the highest grade completed for each round of survey, so the value changes corresponding to the year of the survey. According to the database, the `hgc` variable is revised as in May 1st of each survey year. Thus, we mentioned as the revised May data. In the revised version, we only mention it as revised data to avoid confusion.

\begin{description}
\item[Reviewer 3:]\textcolor{violet}{Abstract: The abstract portrays this work as ”re-creating a textbook example data set.” This doesn’t appear to be quite accurate because there are several notable differences between the end result and the textbook data. Currently, it’s more about demonstrating a procedure for “initial data analysis.”}
\end{description}

* **NEED HELP**
